\tool{}: Specification- and Syntax-based Automated Testing Linguistic Capabilities of NLP Models

### 2023-03-16 paper/fse23/tables/manual-study-table.tex
icse24

\begin{table}[htbp]
\begin{small}
\begin{center}
\caption{\ManualStudyTableCaption}
\resizebox{0.47\textwidth}{!}{
\begin{tabular}{l|l|ccc}
\toprule
\tTask & \tSentType & \tNumTestCases & \tAvgLabelCons & \tAvgLCRel \\
\midrule
\multirow{2}{*}{SA} 
 & SEED & \UseMacro{manual-study-sa-seed-num-sents}
 & \UseMacro{manual-study-sa-seed-label-consistency}
 & \UseMacro{manual-study-sa-seed-lc-relevancy}\\
 & EXP & \UseMacro{manual-study-sa-exp-num-sents}
 & \UseMacro{manual-study-sa-exp-label-consistency}
 & \UseMacro{manual-study-sa-exp-lc-relevancy}\\
\hline
\multirow{2}{*}{HSD} 
 & SEED & \UseMacro{manual-study-hs-seed-num-sents}
 & \UseMacro{manual-study-hs-seed-label-consistency}
 & \UseMacro{manual-study-hs-seed-lc-relevancy}\\
 & EXP & \UseMacro{manual-study-hs-exp-num-sents}
 & \UseMacro{manual-study-hs-exp-label-consistency}
 & \UseMacro{manual-study-hs-exp-lc-relevancy}\\
\bottomrule
\end{tabular}}
\end{center}
\end{small}
\vspace{\ManualStudyTableVSpace}
\end{table}

>>>>

\begin{table}[htbp]
\begin{small}
\begin{center}
\caption{\ManualStudyTableCaption}
\resizebox{0.47\textwidth}{!}{
\begin{tabular}{l|l|cccc}
\toprule
\tTask & \tSentType & \tNumTestCases & \tAvgLabelCons & \tAvgLCRel & \tAvgExpVal \\
\midrule
\multirow{2}{*}{SA} 
 & SEED & \UseMacro{manual-study-sa-seed-num-sents}
 & \UseMacro{manual-study-sa-seed-label-consistency}
 & \UseMacro{manual-study-sa-seed-lc-relevancy}
 & \UseMacro{manual-study-sa-seed-validity}\\
 & EXP & \UseMacro{manual-study-sa-exp-num-sents}
 & \UseMacro{manual-study-sa-exp-label-consistency}
 & \UseMacro{manual-study-sa-exp-lc-relevancy}
 & \UseMacro{manual-study-sa-exp-validity}\\
\hline
\multirow{2}{*}{HSD} 
 & SEED & \UseMacro{manual-study-hs-seed-num-sents}
 & \UseMacro{manual-study-hs-seed-label-consistency}
 & \UseMacro{manual-study-hs-seed-lc-relevancy}
 & \UseMacro{manual-study-hs-seed-validity}\\
 & EXP & \UseMacro{manual-study-hs-exp-num-sents}
 & \UseMacro{manual-study-hs-exp-label-consistency}
 & \UseMacro{manual-study-hs-exp-lc-relevancy}
 & \UseMacro{manual-study-hs-exp-validity}\\
\bottomrule
\end{tabular}}
\end{center}
\end{small}
\vspace{\ManualStudyTableVSpace}
\end{table}

### 2023-03-16 paper/fse23/tables/mtnlp-comp-numbers.tex
icse24

\DefMacro{mtnlp-comp-sa-ours-selfbleu-num-mutate}{50}
\DefMacro{mtnlp-comp-sa-ours-selfbleu-avg}{0.15}
\DefMacro{mtnlp-comp-sa-ours-selfbleu-med}{0.15}
\DefMacro{mtnlp-comp-sa-ours-selfbleu-std}{0.02}
\DefMacro{mtnlp-comp-sa-mtnlp-selfbleu-num-mutate}{32}
\DefMacro{mtnlp-comp-sa-mtnlp-selfbleu-avg}{0.93}
\DefMacro{mtnlp-comp-sa-mtnlp-selfbleu-med}{0.93}
\DefMacro{mtnlp-comp-sa-mtnlp-selfbleu-std}{0.0}
\DefMacro{mtnlp-comp-sa-ours-pdr-num-mutate}{50}
\DefMacro{mtnlp-comp-sa-ours-pdr-avg}{164.7}
\DefMacro{mtnlp-comp-sa-ours-pdr-med}{160.5}
\DefMacro{mtnlp-comp-sa-ours-pdr-std}{10.07}
\DefMacro{mtnlp-comp-sa-mtnlp-pdr-num-mutate}{32}
\DefMacro{mtnlp-comp-sa-mtnlp-pdr-avg}{129.0}
\DefMacro{mtnlp-comp-sa-mtnlp-pdr-med}{129.0}
\DefMacro{mtnlp-comp-sa-mtnlp-pdr-std}{0.0}
\DefMacro{mtnlp-comp-hs-ours-selfbleu-num-mutate}{50}
\DefMacro{mtnlp-comp-hs-ours-selfbleu-avg}{0.15}
\DefMacro{mtnlp-comp-hs-ours-selfbleu-med}{0.15}
\DefMacro{mtnlp-comp-hs-ours-selfbleu-std}{0.01}
\DefMacro{mtnlp-comp-hs-mtnlp-selfbleu-num-mutate}{40}
\DefMacro{mtnlp-comp-hs-mtnlp-selfbleu-avg}{0.93}
\DefMacro{mtnlp-comp-hs-mtnlp-selfbleu-med}{0.93}
\DefMacro{mtnlp-comp-hs-mtnlp-selfbleu-std}{0.0}
\DefMacro{mtnlp-comp-hs-ours-pdr-num-mutate}{50}
\DefMacro{mtnlp-comp-hs-ours-pdr-avg}{206.6}
\DefMacro{mtnlp-comp-hs-ours-pdr-med}{208.0}
\DefMacro{mtnlp-comp-hs-ours-pdr-std}{7.12}
\DefMacro{mtnlp-comp-hs-mtnlp-pdr-num-mutate}{40}
\DefMacro{mtnlp-comp-hs-mtnlp-pdr-avg}{131.0}
\DefMacro{mtnlp-comp-hs-mtnlp-pdr-med}{131.0}
\DefMacro{mtnlp-comp-hs-mtnlp-pdr-std}{0.0}

>>>>

\DefMacro{adv-comp-sa-model-under-test}{textattack/bert-base-uncased-SST-2}
\DefMacro{adv-comp-sa-alzantot-num-adv}{20}
\DefMacro{adv-comp-sa-alzantot-num-adv}{20}
\DefMacro{adv-comp-sa-alzantot-selfbleu-med}{0.373}
\DefMacro{adv-comp-sa-alzantot-selfbleu-avg}{0.373}
\DefMacro{adv-comp-sa-alzantot-selfbleu-std}{0.0}
\DefMacro{adv-comp-sa-alzantot-pdrcov-med}{170}
\DefMacro{adv-comp-sa-alzantot-pdrcov-avg}{170.0}
\DefMacro{adv-comp-sa-alzantot-pdrcov-std}{0.0}
\DefMacro{adv-comp-sa-bert-attack-num-adv}{25}
\DefMacro{adv-comp-sa-bert-attack-num-adv}{25}
\DefMacro{adv-comp-sa-bert-attack-selfbleu-med}{0.438}
\DefMacro{adv-comp-sa-bert-attack-selfbleu-avg}{0.438}
\DefMacro{adv-comp-sa-bert-attack-selfbleu-std}{0.0}
\DefMacro{adv-comp-sa-bert-attack-pdrcov-med}{178}
\DefMacro{adv-comp-sa-bert-attack-pdrcov-avg}{178.0}
\DefMacro{adv-comp-sa-bert-attack-pdrcov-std}{0.0}
\DefMacro{adv-comp-sa-pso-num-adv}{25}
\DefMacro{adv-comp-sa-pso-num-adv}{25}
\DefMacro{adv-comp-sa-pso-selfbleu-med}{0.411}
\DefMacro{adv-comp-sa-pso-selfbleu-avg}{0.411}
\DefMacro{adv-comp-sa-pso-selfbleu-std}{0.0}
\DefMacro{adv-comp-sa-pso-pdrcov-med}{178}
\DefMacro{adv-comp-sa-pso-pdrcov-avg}{178.0}
\DefMacro{adv-comp-sa-pso-pdrcov-std}{0.0}
\DefMacro{adv-comp-sa-ours-num-adv}{323}
\DefMacro{adv-comp-sa-ours_exp-num-adv}{50}
\DefMacro{adv-comp-sa-ours-selfbleu-med}{0.437}
\DefMacro{adv-comp-sa-ours-selfbleu-avg}{0.435}
\DefMacro{adv-comp-sa-ours-selfbleu-std}{0.005}
\DefMacro{adv-comp-sa-ours-pdrcov-med}{264}
\DefMacro{adv-comp-sa-ours-pdrcov-avg}{262.0}
\DefMacro{adv-comp-sa-ours-pdrcov-std}{2.739}
